---
title: "Writing tutorials"
author: "Eric Koncina"
date: "`r Sys.Date()`"
output:
  unilur::tutorial_html_solution:
    suffix: ""
    toc: yes
pkgdown:
  as_is: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)


```

## The `unilur` tutorial formats

To start writing your first practical for students, create a new Rmarkdown file using the template provided by `unilur`.
The yaml header will contain the following output formats:

```
output:
  unilur::tutorial_html: default
  unilur::tutorial_pdf: default
  unilur::tutorial_html_solution: default
  unilur::tutorial_pdf_solution: default
```

Use the Rstudio dropdown knit button to render the desired file. To allow the creation of two distinct files (with and without solutions) from a single Rmarkdown file, the output file will end with a suffix which can be adjusted in the YAML header.

The default values of the `suffix` argument are:

- **`_question`** for `unilur::tutorial_html` and `unilur::tutorial_pdf`
- **`_solution`** for `unilur::tutorial_html_solution` and `unilur::tutorial_pdf_solution`
- **`_answer`** for `unilur::answer_rmd`

## Solutions

Answers or solutions are written within a [code chunk](http://rmarkdown.rstudio.com/authoring_rcodechunks.html) with the `solution = TRUE` option. The content of these chunks will be wrapped within a green box (read the custom boxes article to change the appearance).

For example, if you write the following question and supply the `solution = TRUE` option chunk to the answer:

    - What is the mean speed reported in the `cars` dataset?
    
    `r ''````{r, solution = TRUE}
    mean(cars$speed)
    ```

You will generate the following output using the `unilur::tutorial_html_solution` format:

- What is the mean speed reported in the `cars` dataset?

```{r, solution = TRUE}
 mean(cars$speed)
```

If you render the same file using `unilur::tutorial_html`, the green box containing your expected answer will not appear.

```{r, echo = FALSE}
knitr::opts_template$set(advice = list(box.title = "Advice",
                                         box.body = list(fill = "pink"),
                                         box.icon = icon::ii_information()))
```

```{block, opts.label = "advice"}
To highlight some content, you can also include it in custom boxes: have a look at the dedicated [article](custom-boxes.html) to learn how to create them.
```
